Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex

\documentclass[10pt,twocolumn]{article} 
\usepackage{simpleConference}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{url,hyperref}

@@

@@

@@

>>>>

\documentclass[11pt,twocolumn]{article} 
\usepackage{simpleConference}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{url,hyperref}

@@

Note that by constructing morphological chains rather than just finding segmentations, more information is gained about the words tested. Generating the chain, in addition to segmenting a word, also finds the base word and predicts the order in which the morphemes attach to the base word.

@@

In the unsupervised version of our model, we observe words in a wordlist with their word count of occurrences. Additionally, we have access to a large corpus of text from which we can obtain semantic information. Our objective is to generate morphological segmentations, which we do by generating morphological chains, as given by Narasimhan et al.

@@

\begin{description}
    \item[Affixes] Prefixes and suffixes appear in many words. For a given word with its potential parent, the affix removed can be compared against a precompiled list of potential affixes. This allows the model to learn which affixes are real and apply them to other cases with the same potential affix.
    \item[Affix Correlation] Similar to comparing affixes across words, we can use the joint distribution of words and their potential affixes. There is a correlation between affixes that can usually attach to the same stem, often corresponding to the part of speech. For example, the participles formed from the suffixes -ing and -ed usually occur together. For candidates with an affix that is correlated with another affix, we can check if the parent with the other affix also occurs in the observed wordlist.
    \item[Semantic Similarity] Morphologically related words should have similar meanings. We measure the \emph{cosine similarity} between the word and its candidate parent. % TODO wordvector citation?
        It has been shown that words can be mapped to word vectors in a reasonably-sized dimensional space such that semantically similar 
\end{description}
